---
title: "Elo Odds"
output: html_document
runtime: shiny_prerendered
---

```{r setup, include = FALSE}
library(tidyverse)
library(DT)
knitr::opts_chunk$set(echo = FALSE)
```

Here comes the introduction!

```{r data, message = FALSE, cache = TRUE, cache.extra = file.info("D:/Rstuff/shiny-server/elo-odds/data/allEloOdds.rds")$mtime}
input_data <- "D:/Rstuff/shiny-server/elo-odds/data/allEloOdds.rds"

#```{r data, message = FALSE, cache = TRUE, cache.extra = file.info("/home/lukas/Rprojects/BettingElo/data/allEloOdds.rds")$mtime}
#input_data <- "/home/lukas/Rprojects/BettingElo/data/allEloOdds.rds"

# available to each user session
# input_data <- "D:/Rstuff/oddScrape/data/allEloOdds.rds" #needs to be updated for the server to something like "/home/lukas/Rprojects/BettingElo/data/allEloOdds.rds"

eloOdds <- readRDS(input_data)
colnames(eloOdds) <-  gsub(pattern = "_odds", replacement = "", colnames(eloOdds))
```


```{r user_input}
inputPanel(
  uiOutput("ui")
)
DT::dataTableOutput("tbl")
```

```{r creat_output, context = "server"}

output$ui <- renderUI({
  dateInput('date',
            label = paste('Choose date:'),
            value = as.character(max(eloOdds$Date)),
            min = min(eloOdds$Date), max = max(eloOdds$Date),
            format = "dd.mm.yyyy",
            startview = 'week', weekstart = 1
  )
}) 

# renderTable({
#   eloOdds %>% 
#   filter(Date == input$date)
#   },
#   striped = TRUE,
#   digits = 2) 

output$tbl <- DT::renderDataTable({
  out <- eloOdds %>% filter(Date == input$date) %>% 
    mutate(Date = format(as.Date(Date), "%d.%m.%Y"))
  DT::datatable(out,
                extensions = 'Buttons', 
                options = list(
                  dom = 'Bft',
                  buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                  pageLength = nrow(out)
                ),
                rownames = FALSE
  ) %>% 
    #DT::formatRound(c("Home", "Draw"), 2)
    DT::formatRound(5:10, 2)
})

```

Some stuff at the end.



