---
title: 'AGES: Coffee model'
output:
  html_document:
    theme: readable
    highlight: tango
runtime: shiny
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(scales)
library(shiny)
```

This interactive page allows you to calculate different scenarios regarding coffee consumption at AGES. Your can vary several parameters to analyse infinite possible situations.

## Price-per-cup-calculator

Here you can compute the estimated break-even price per cup of coffee. Costs for the coffee machine (maintainance etc.) are not taken into account. A recent "long-term" study suggests that a kg of coffee beans results in 85 cups of delicious coffee (data not shown).

The break-even price per cup of coffee is calculated using the price per pack, the size of the pack and the estimated cups of coffee gained from one kg of beans.
```{r ppcc}
inputPanel(
  numericInput("pack_price", label = "Price per pack (EUR):",
               value = 10, min = 0, step = 0.01, width = "120px"),
  # br(),
  numericInput("pack_size", label = "Size of pack (g):",
               value = 1000, min = 0, step = 1, width = "100px"),
  # br(),
  numericInput("expect_cups_kg", label = "Expected cups per kg of coffee beans:",
               min = 1, value = 85, step = 1)
)

renderText({
  price_cup <- ceiling(input$pack_price / input$expect_cups_kg * 1000 / input$pack_size * 100) / 100
  HTML(paste0("The price per cup is ", price_cup, " EUR."))
})
```

## Coffee..mhhmmmmm

```{r coffee}
inputPanel(
  numericInput("avg_coffee_cups", label = "Average daily coffee cup consumption:",
               value = 10, min = 0, step = 1, width = "90%"),
  
  numericInput("net_price", label = "Price of coffee beans per cup (in EUR):",
               value = 0.12, min = 0, step = 0.01, width = "90%"),

  numericInput("price_cup", label = "Price per cup (in EUR):",
               value = 0.15, min = 0, step = 0.01, width = "60%"),
  
  numericInput("stealing_rate", label = "Stealing rate:",
               value = 0.1, min = 0, max = 1, step = 0.01, width = "50%")
)

savings <- reactive({
  workdays_per_year <- 240
  
  savings <- (input$avg_coffee_cups * input$price_cup * (1 - input$stealing_rate) - input$avg_coffee_cups * input$net_price) * 1:240
  
  savings
})

renderText({
  paste0("The average savings per Day are ", round(savings()[1], 2), " EUR.")
})

renderPlot({
  df0 <- data.frame(days = 1:240, savings = savings(), stringsAsFactors = FALSE)
  
  ggplot(df0, aes(x = days, y = savings, group = 1)) +
  geom_line(colour = "blue") +
  labs(list(x = "Working days", y = "Savings (in EUR)")) +
  scale_y_continuous(breaks = pretty_breaks(10), expand = c(0, 0)) +
  theme_minimal()
})
```




